\chapter*{Preface}
Welcome to the RIKEN AICS Annual Report for 2015.

We are very excited about this annual report that illustrates the significant accomplishments that our AICS teams have achieved this year using the supercomputer K.

RIKEN AICS is the Japanese flagship research institution in computer science and computational science. It is an organization charged with operating the K computer. AICS aims to establish international research center which produces breakthroughs through collaboration between computational and computer sciences. Plotting and developing Japan's strategy for HPC, which includes the development of the post K computer, is also an important mission of AICS.

The K computer demonstrates an extraordinary level of stability and provided exceptional service to science, engineering, and research communities. This is due to the dedicated efforts of the teams of the operations and computer technologies division.

In many science and engineering areas, we see many great results since the K computer started full service in September 2012. Many projects that use the K computer would be difficult or impossible to do elsewhere. AICS research teams have developed common computing techniques for utilization of the K computer, and also coded the very efficient parallelized application program packages. Now the K computer is being used in many different fronts and extending the boundaries of computational science. As you see in this report, our AICS research teams made a great contribution to produce many of these exciting results.

The K computer significantly enhanced the resolution both in precision and the system size through massively parallel computation. In addition, capacity computing opened the possibility of prediction in complex and non-linear/chaotic phenomena. We are now tackling highly complex scientific and social problems with inherent uncertainties and unpredictability. The way to deal with such uncertainty is to simultaneously run multiple ensembles, using many different combinations of parameters, and thus be able to explore the solution. The K computer significantly enhanced the capacity computing in addition to the capability computing.

AICS is also charged with the development of the post K computer. The flagship 2020 project division is carrying out the development of the post K computer. The post K computer will be used to work on innovative solutions to current scientific and social issues. The development of application codes to run on the post K computer is also a mission of the project.

We hope you enjoy reading all the wonderful advances made by RIKEN AICS. We look forward to continuing our activities for more fundamental and bigger science and engineering for years to come.

\vspace{1cm}

\noindent
Kimihiko Hirao\\
Director, RIKEN AICS
