\chapter*{}

This part presents the research activity of the Research Division of RIKEN Advanced Institute for Computational Science (AICS) for the period of 1 April 2015 to 31 March 2016.

This is the sixth year for AICS since its foundation in 2010.  The Research Division continued to operate with 16 teams and 3 units as established in 2012.  As of 1 April 2014, the number of researchers in the Division was 126 in total.

The research activity in this fiscal year resulted in ??? journal papers, ??? conference reports, ??? invited talks, ??? posters and presentations, ??? patents and deliverables.

Memorable awards bestowed upon AICS researchers included No. 1 ranking on Graph500 in June and November 2015, back from No. 2 in November 2014.  Combined with the No. 4 position on Top500 Ranking and No. 2 on HPCG ranking maintained through 2015, they continued to illustrate the well-balanced and versatile performance of the K computer in its 4th year of operation.

Many research-related events took place in this fiscal year.  The 6th AICS International Symposium, which became an annual event at Kobe, was held on 22 – 23 February 2016 under the title “Plans and future for international collaborations on extreme scale computing”.  AICS also hosted “Lattice 2015 – the 33rd International Symposium on Lattice Field Theory” on 14 – 18 July, 2015, a major conference in the field of computational particle physics.

We hope that this volume conveys the excitement of research and development at the forefront of computational and computer science being conducted at Research Division of RIKEN AICS to readers.

\vspace{1cm}

\noindent
July 2016

\begin{flushright}
Akira Ukawa\\
Research Division Director\\
and Deputy Director\\
RIKEN AICS
\end{flushright}
